
---
title: "Day16_MLflow"
output:
  html_document:
    toc: true
---

# MLflow Starting with experiments
### Attach cluster to notebook

I have named my notebook as _Day16_MLflow_ using *R* Language.

If you are using Databricks Runtime cluster without *ML* suffix (Databricks runtime for Machine Learning), you need to install the following packages.

Installation (if your cluster is not Databricks runtime for Machine Learning)
- go to Cluster
- select Libraries
- Select "% install new"
- For R environemnt select CRAN repository and select the package name _mlflow_
- click ok and wait.
- after successfull installation, return to this notebook to load the library

```{r}
library(mlflow)
install_mlflow()
```

Now we can use MLflow tracking API to capture runs (with  artifacts) for this notebook

```{r}
mlflow_start_run()
```


```{r}
# Log a parameter (key-value pair)
mlflow_log_param("test_run_nof_runs_param1", 5)

# Log a metric; metrics can be updated throughout the run
mlflow_log_metric("RMSE", 2, step = 1)
mlflow_log_metric("RMSE", 4, step = 2)
mlflow_log_metric("RMSE", 6, step = 3)
mlflow_log_metric("RMSE", 8, step = 4)
mlflow_log_metric("RMSE", 1, step = 5)
# Log an artifact (output file)

write("This is R code from Azure Databricks notebook", file = "output.txt")

mlflow_log_artifact("output.txt")

```


```{r}
mlflow_end_run()
```

You can also in advance create an experiment and use it here.
Presume, that you have created a "new experiment" and named it: RunExperiment.
Let's create a model and wrapping it in MLflow

```{r}
library(mlflow)
library(glmnet)
library(carrier)
```


```{r}
library(SparkR)

data <- read.df("/FileStore/Day16_wine_quality.csv", source = "csv", header="true")

display(data)
data <- as.data.frame(data)
```


```{r}
#detaching the package due to data type conflicts
detach("package:SparkR", unload=TRUE)
```


```{r}
# Split the data into training and test sets. (0.75, 0.25) split.
sampled <- sample(1:nrow(data), 0.75 * nrow(data))
train <- data[sampled, ]
test <- data[-sampled, ]

# The predicted column is "quality" which is a scalar from [3, 9]
train_x <- as.matrix(train[, !(names(train) == "quality")])
test_x <- as.matrix(test[, !(names(train) == "quality")])
train_y <- train[, "quality"]
test_y <- test[, "quality"]

alpha <- mlflow_param("alpha", 0.5, "numeric")
lambda <- mlflow_param("lambda", 0.5, "numeric")
```


```{r}
mlflow_start_run()

model <- glmnet(train_x, train_y, alpha = alpha, lambda = lambda, family= "gaussian", standardize = FALSE)
predictor <- crate(~ glmnet::predict.glmnet(!!model, as.matrix(.x)), !!model)
predicted <- predictor(test_x)

rmse <- sqrt(mean((predicted - test_y) ^ 2))
mae <- mean(abs(predicted - test_y))
r2 <- as.numeric(cor(predicted, test_y) ^ 2)

message("Elasticnet model (alpha=", alpha, ", lambda=", lambda, "):")
message("  RMSE: ", rmse)
message("  MAE: ", mae)
message("  R2: ", r2)

mlflow_log_param("alpha", alpha)
mlflow_log_param("lambda", lambda)
mlflow_log_metric("rmse", rmse)
mlflow_log_metric("r2", r2)
mlflow_log_metric("mae", mae)

mlflow_log_model(
predictor, 
artifact_path = "model", 
registered_model_name = "wine-quality")

mlflow_end_run()
```

